---
title: "Exercise 1"
author:
  - name: Johannes Signer
    orcid: 0000-0002-1771-7775
    email: jmsigner@gmail.com
date: last-modified
format: html
---

## Exercise
### Background

The aim of this exercise is to understand the effect of ignoring bursts. Remember a burst has equal the same time between observations. For example, if we aim to have a GPS position every one hour, then one burst lasts until there is a time diffrence of > 1 hour between two GPS fixes. 

### Data

Use again the fisher data set and data for Leroy.

### Task
Compute the step lengths of the first steps of bursts and the last steps of bursts. And test, if their means are different.

### Hints

We have not talked about step lengths in module 1 (it is covered in module 3). If unsure how to calcualte the step lengths, you can use the function `step_lengths()` on any `track`-object.

For example

```{r}
library(amt)
data(deer) # loeads the deer data set
head(deer) |> step_lengths()
```


## Solution 

First load the data and create a track:

```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE

library(amt)
library(tidyverse)

dat <- read_csv(here::here("data/fisher.csv"))

leroy <- filter(dat, name == "Leroy")
leroy <- make_track(leroy, x_, y_, t_)
```

Then we have to resample the track to a suitable rate, here we choose 15 min, after looking at `summarize_sampling_rate()` and calculate the step lengths. 

```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE

leroy <- track_resample(leroy, rate = minutes(15), tolerance = minutes(2))
leroy1 <- leroy %>% mutate(sl = step_lengths(.))
```

Now we can summarize the step length of the first step and last step for each burst and create a boxplot to visualize the result. 

```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE
leroy1 |> group_by(burst_) |> 
  summarize(fs = head(sl, 1), ls = tail(sl, 1)) |> 
  pivot_longer(-burst_) |> 
  ggplot(aes(name, value)) + geom_boxplot()
```

It appears that last steps of bursts are on average longer than the first steps. There is no biological reason to assume this.


Next, lets repeat the same analysis with acknowleding bursts. I am presenting here an approach that useses the `nest()` function from the `tidyverse()`. If you have not used this before, I will talk in much more detail about this in module 7. 

```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE
# Let's repeat the same analysis, but this time with bursts now for calculating
# step lengths (we need to nest our data here)
leroy2 <- leroy1 |> nest(data = -burst_) |> 
  mutate(data = map(data, ~ mutate(.x, sl = step_lengths(.x)))) |> 
  unnest(cols = data)

leroy2 |> group_by(burst_) |> 
  summarize(fs = head(sl, 1), ls = tail(sl, 2)[1]) |> 
  pivot_longer(-burst_) |> 
  ggplot(aes(name, value)) + geom_boxplot()

```

