---
title: "Data Cleaning Exercise"
author: 
  - name: Brian J. Smith
    orcid: 0000-0002-0531-0492
    email: brian.smith@usu.edu
date: last-modified
format: html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

Let's apply what we've learned about data cleaning. Refer to the lecture slides (<a href="05a_lecture.html" target="_blank" rel="noopener noreferrer">05a_lecture.html</a>) and the walkthrough code (`05b_walkthrough.R`) as a refresher.

We encourage you to use your own data for this exercise. We will be available while you are working to answer any questions.

If you don't have your own data, you can use example data built into `amt`. You can access the fisher data like this:

```{r amt_fisher, eval = FALSE}
# Load `amt`
library(amt)

# Location data as 'track_xyt'
dat <- amt_fisher

```

You likely have more than one individual in your own data, and `amt_fisher` also has 4 individuals. Subset to just one individual for this (I recommend "Ricky T").

## Instructions

1. Load in your data or the `amt_fisher` dataset. If you're working with your own data, format it as a `track_xyt` object using `amt::make_track()`.
  
2. Clean these data! For the `amt_fisher` data, you can assume the data only cover the deployment, so you can ignore step 1 and step 8. You decide whether you think there is a capture effect in the data! Justify why you chose the cleaning parameters that you do.
