---
title: "Exercise 3"
author:
  - name: Johannes Signer
    orcid: 0000-0002-1771-7775
    email: jmsigner@gmail.com
date: last-modified
format: html
---

## Exercise
### Data
Use tracking data of one red deer from northern Germany. The data can be obtained with with `data(deer)` in `amt`. You can get a forest layer for the study area with `get_sh_forest()`, where 1 is encoded as forest and 0 as non-forest or open. 

### Task
Compute the step lengths and turn angles for the tracked deer. Try to answer the following questions: 

1. Do step lengths differ for steps that start during day or during night? 
2. Do steps that start and end in the forest are different from steps that start and end in the open or have start and end in different habitat?

*A visual inspection/comparison is sufficient*. 

## Solution 

First load the data and create a track:

```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE

library(amt)
library(tidyverse)

data(deer)
forest <- get_sh_forest()
```


Next lets transform to steps and calculate time of day. 

```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE

deer1 <- deer |> steps_by_burst() |> time_of_day(where = "both")

```

Now we can plot steps that start during day and during night. 


```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE

deer1 |> 
  ggplot(aes(tod_start_, sl_)) + 
  geom_boxplot() +
  theme_light()

```

Finally, lets annotate steps with covariates


```{r}
#| code-fold: true
#| code-summary: "Show solution"
#| eval: FALSE

deer1 |> 
  extract_covariates(forest, where = "both") |> 
  mutate(
    step_type = case_when(
      forest_start == 1 & forest_end == 1 ~ "forest", 
      forest_start == 0 & forest_end == 0 ~ "open", 
      forest_start != forest_end ~ "mixed"
    )
  ) |> 
  ggplot(aes(step_type, sl_)) + geom_boxplot()

```
